Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Deleted extra sections at bottom
Add Data section.

\subsection*{The Experiment}
We construct an experiment to test the efficacy of a predictive model. 
We would like to know {\em a priori} the true similarity for a pair of items.
For either true similarity metric, $TrueSim$ is a theoretical construct and not 
something we have access to in the real world. Fortunately, we can achieve good
approximations of $TrueSim$ given sufficient data. We therefore define $GoldSim$
= $Sim_N$ where $N$ is a number large enough that $GoldSim \approx TrueSim$.

@@

\section*{Score-based Approach}
\subsection*{Probabilistic Model}

@@

\section*{Ratings-based Approach}
\subsection*{Probabilistic Model}

@@

\subsection*{The Technique}

>>>>

\subsection*{Data}
In the following section, we will describe an off-line experiment used to
evaluate our similarity estimators. But first, we provide some details about the
data used for this work. The data, originally from Amazon.com, was acquired from
the Stanford Network Analysis Project\footnote{http://snap.stanford.edu}. It
consists of ~5.6M ratings by ~1.2M users of ~600k music items (e.g. albums and
songs). Each rating is from 1 to 5 stars and is associated with a particular
user and item at a particular time.  For practical reasons, we focus our work on
two subsets of this data. The first consists of item pairs having at least 40
common reviewers (i.e. users that have provided a rating for the item). The
second consists of item pairs having at least 80 common reviewers. As discussed
below, we must confine ourselves to item pairs that have many common reviewers
in order to determine a good approximation of the their true similarity.

\subsection*{Experiment}
Ideally, we would know {\em a priori} the true similarity for a set of item
pairs. But both $TrueSimRand$ and $TrueSimPref$ are theoretical constructs and
not metrics we have access to in the real world.  Fortunately, we can achieve
good approximations of either $TrueSim$ given sufficient data. We therefore
define $GoldSim$ = $Sim_N$ where $N$ is a number large enough that $GoldSim
\approx TrueSim$.

@@

\section*{Score-based Method}
\subsection*{Probabilistic Model}

@@

\section*{Ratings-based Method}
\subsection*{Probabilistic Model}

@@

\subsection*{Technique and Results}
